---
title: "p8105_hw2_jw3726"
author: "Jiabei Wang"
date: "October 4th 2018"
output: github_document
---
##problem 1
```{r setup}
library(tidyverse)
library(readxl)
NYCTransit_data = read_csv(file = "./NYC_Transit_Subway_Entrance_And_Exit_Data (1).csv")  %>%
janitor::clean_names() %>%
select(line,station_name,station_latitude,station_longitude,route1:route11,entry,vending,entrance_type,ada,ada_notes) %>%
mutate(entry = recode(entry, "YES" = TRUE,"NO" = FALSE ))
##the dataset now contains variables retain line, station name, station latitude,station longitude, routes served, entry, vending, entrance type, and ADA compliance. (not finish)

library(dplyr)
distinct_station = distinct(NYCTransit_data,station_name,line,.keep_all = TRUE) 
##there are 450 distinct stations

filter(distinct_station, ada == TRUE)
##there are 84 stations that are ada compliant 

without_vending = filter(NYCTransit_data, vending == "NO")
without_vending_allow_entrance = filter(without_vending,entry == TRUE )
nrow(without_vending_allow_entrance)/nrow(without_vending)
##The proportion is 0.377

tidy_transit_data = gather(distinct_station,key = route_number, value = route_name, route1:route11) 
distinct_serve_A = filter(tidy_transit_data, route_name == "A")
##there are 60 distinct stations serve A train. 

ADA_compliant = filter(distinct_serve_A, ada == TRUE) 
##there are 17 ADA compliant
```
There are 1868 observations. There are `r nrow(distinct(NYCTransit_data,station_name,line,.keep_all = TRUE)) `distinct stations. There are `r nrow(filter(distinct_station, ada == TRUE))`that are ada compliant. The proportion of station entrances / exits without vending allow entrance is 0.377. There are 60 distinct stations serve A train. There are 17 ADA compliant

##problem2
```{r}
library(readxl)
Trash_Wheel_data = readxl::read_excel("HealthyHarborWaterWheelTotals.xlsx",range = 'A2:N338') %>%
  janitor::clean_names() %>%
filter (!is.na(dumpster) ) %>% ##omit colums containing notes (how to specify?)
##round sports_balls to integer and convert it to integer variable
 mutate(sports_balls = round(sports_balls,digits = 0) ) 
integer_trash_wheel = as.integer(Trash_Wheel_data$sports_balls) 

  
```

```{r}
precipitation_2017 = readxl::read_excel("./HealthyHarborWaterWheelTotals.xlsx",sheet = 4, range = "A2:B15") %>%
janitor::clean_names() %>%
  ##omit rows without precipitation data
  filter(!is.na(total)) %>%
  ##add a variable name
mutate(year = "2017")

precipitation_2016 = readxl::read_excel("./HealthyHarborWaterWheelTotals.xlsx",sheet = 5, range = "A2:B15" ) %>%
janitor::clean_names() %>%
  ##omit rows without precipitation data
   filter(!is.na(total))  %>%
  ##add a variable name
mutate(year = "2016")
##combine datasets
bind_2016_2017 = bind_rows(precipitation_2017, precipitation_2016 ) 
##convert month to a character variable
mutate(bind_2016_2017, month.name[month]) 

```

the number of observations in dataset precipitation_2017 is `r dim(precipitation_2017)` , and there are `r dim(precipitation_2016)`observations in dataset precipitation_2016 precipitation_2016. The total precipitation in 2017 is `r sum(precipitation_2017$total)/2`.
The median number of sports ball is `r median( filter(Trash_Wheel_data, year == 2016)$sports_balls)`. 
The key variables are dumpster, weight_tons, and volume_cubic_yards. 

##problem3
```{r}
library(p8105.datasets)
data(brfss_smart2010) 
## appropriate variable name
brfss_smart2010 = janitor::clean_names(brfss_smart2010)
##focus on "Overall Health topic"
Overall_Health_data = filter(brfss_smart2010,topic == "Overall Health")
##exclude some variables
Overall_Health_data = select(Overall_Health_data, year, locationabbr, locationdesc, response, data_value)
##structure data
Overall_Health_data = spread(Overall_Health_data, key = response, value = data_value)
Overall_Health_data = janitor::clean_names(Overall_Health_data) %>% 
##create a new variable

mutate(proportion = (excellent + very_good)) 
  
##how many unique stations
distinct_station = distinct(Overall_Health_data, locationabbr,.keep_all = TRUE)
distinct_station = distinct(Overall_Health_data, locationdesc,.keep_all = TRUE)
tail(names(sort(table(brfss_smart2010$locationabbr))),1)
year_2002 = filter(Overall_Health_data, year == 2002)
##median
median(Overall_Health_data$excellent, na.rm = TRUE)
##histogram
ggplot(year_2002, aes(x = excellent)) + 
  geom_histogram()
location_NY = filter(Overall_Health_data, locationdesc =="NY - New York County"|locationdesc == "NY - Queens County" )
ggplot(location_NY, aes(x = year, y = excellent)) + 
  geom_point(aes(color = locationdesc))

```
the number of unique station is `r nrow(distinct_station)`
Yes, every state is represented, since there are 51 states in the US.There are 404 locations. NJ is observed the most.
The median of the "Excellent" is `r median(year_2002$excellent, na.rm = TRUE)`
the most frequent state is `r tail(names(sort(table(brfss_smart2010$locationabbr))),1)`
From the histogram, the excellent centered between 20 and 30, and there is outlier is centered around 40.
From the scatterplot, NY_Quennes County lie between 15 to 20, and New York country mainly lie between 25 to 30. 
  


